Bioverse: Potentially Observable Exoplanet Biosignature Patterns Under the UV Threshold Hypothesis for the Origin of Life

### 2025-02-05 src/tex/ms.tex
oops typo

\rev{Then, we turn to a metric which measures the information gain of sampling: the Bayes factor \cite{Jeffreys1939}.
The posterior evidence for the null hypothesis $H_{\mathrm{null}}$ is given by the Bayes' theorem:
\begin{equation}
\label{eq:bayesHnull}
    P(H_{\mathrm{null}}|Y) = \frac{P(Y|H_{\mathrm{null}})P(H_{\mathrm{null}})}{P(Y)}
\end{equation}
and the posterior evidence for the NUV hypothesis:
\begin{equation}
    \label{eq:bayesHone}
        P(H_1|Y) = \frac{P(Y|H_1)P(H_1)}{P(Y)}~.
\end{equation}
Computing the distributions given by equations \ref{eq:bayesHnull} and \ref{eq:bayesHone} requires the distributions of likelihoods, given in equations \ref{eq:semian:likelihoodHnull} and \ref{eq:semian:likelihoodH1}, as well as the prior distributions for each hypothesis ($P(H_{\mathrm{null}})$ and $P(H_{1})$) and for the sample ($P(H_{1})$).
}
\rev{
Appart from the caveat that the likelihood for $H_{1}$ cannot be expressed analytically due to being conditioned by n_{\lambda} (equation \ref{eq:semian:likelihoodH1}), computing posterior probabilities is challenging due to the unknown priors.
}

>>>>

\rev{Then, we turn to a metric which measures the information gain of sampling: the Bayes factor \cite{Jeffreys1939}.
The posterior evidence for the null hypothesis $H_{\mathrm{null}}$ is given by the Bayes' theorem:
\begin{equation}
\label{eq:bayesHnull}
    P(H_{\mathrm{null}}|Y) = \frac{P(Y|H_{\mathrm{null}})P(H_{\mathrm{null}})}{P(Y)}
\end{equation}
and the posterior evidence for the NUV hypothesis:
\begin{equation}
    \label{eq:bayesHone}
        P(H_1|Y) = \frac{P(Y|H_1)P(H_1)}{P(Y)}~.
\end{equation}
Computing the distributions given by equations \ref{eq:bayesHnull} and \ref{eq:bayesHone} requires the distributions of likelihoods, given in equations \ref{eq:semian:likelihoodHnull} and \ref{eq:semian:likelihoodH1}, as well as the prior distributions for each hypothesis ($P(H_{\mathrm{null}})$ and $P(H_{1})$) and for the sample ($P(H_{1})$).
}
\rev{
Apart from the caveat that the likelihood for $H_{1}$ cannot be expressed analytically due to being conditioned by n_{\lambda} (equation \ref{eq:semian:likelihoodH1}), computing posterior probabilities is challenging due to the unknown priors.
}
